cardinalR: Generating interesting high-dimensional data structures

### 2025-08-22 paper-cardinalR.Rmd
Updated application section with langevitour output

The following code generates a dataset of five clusters, positioned with equal inter-cluster distances in $4\text{-}D$ space (Figure \@ref(fig:fig-highd-proj)).

@@

```{r, eval=FALSE}
langevitour::langevitour(five_clusts[, -5])
```

@@

```{r, label = "fig-highd-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green."}
#| fig-width: 15
#| fig-height: 5

>>>>

The following code generates a dataset of five clusters, positioned with equal inter-cluster distances in $4\text{-}D$ space (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:highd-data)"} else { "Figure \\@ref(fig:highd-proj)"})`).

@@

```{r highd-data, eval=knitr::is_html_output(), fig.cap="`langevitour` output showing five synthetic clusters with distinct geometric structures: a helical spiral, a hemisphere, a uniform cube, a cone, and a Gaussian cluster."}

langevitour::langevitour(five_clusts[, -5], group = five_clusts$cluster, levelColors = c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e'))
```

@@

```{r highd-proj, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green."}
#| fig-width: 15
#| fig-height: 5

### 2025-08-22 paper-cardinalR.tex
Updated application section with langevitour output

The construction is based on a regular grid in spherical coordinates with \((p-1)\) angular variables. Specifically:

\begin{itemize}
\tightlist
\item
  For dimensions \(j = 1, \dots, p-2\), the polar angles are defined on \([0, \pi]\).
\item
  For the last angle (\(j = p-1\)), the azimuthal angle is defined on \([0, 2\pi]\).
\end{itemize}

@@

The following code generates a dataset of five clusters, positioned with equal inter-cluster distances in \(4\text{-}D\) space (Figure \ref{fig:fig-highd-proj}).

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-highd-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.}\label{fig:fig-highd-proj}
\end{figure}

>>>>

The construction is based on a regular grid in spherical coordinates with \((p-1)\) angular variables. Specifically, for dimensions \(j = 1, \dots, p-2\), the polar angles are defined on \([0, \pi]\). For the last angle (\(j = p-1\)), the azimuthal angle is defined on \([0, 2\pi]\).

@@

The following code generates a dataset of five clusters, positioned with equal inter-cluster distances in \(4\text{-}D\) space (Figure \ref{fig:highd-proj}).

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/highd-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.}\label{fig:highd-proj}
\end{figure}
